---
title: "Mapping out DC Landmarks"
description: |
  This short project showcases where certain famous DC landmarks are located in the District. 
author:
  - name: Arielle Ostry
    url: https://ostryarielle.wixsite.com/mysite
date: 04-20-2021
output:
  distill::distill_article:
    self_contained: false
categories:
  - data
  - maps
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Load packages
library(tidyverse)
library(lubridate)
library(readxl)
library(janitor)
library(glue)
library(leaflet)
library(RColorBrewer)
library(htmlwidgets)
library(htmltools)
library(tigris)
library(tmap)
library(tmaptools)
library(rmarkdown)
options(tigris_class = "sf")

#your code here

Landmarks_DC <- read_excel("Landmarks_DC.xlsx")

```

**Our Landmarks Table**  
Featuring four popular DC locations including the Lincoln Memorial, Union Station, the National Portrait Gallery, and the U.S. Capitol.

```{r}
head(Landmarks_DC)
```


**Our Map**  
With the information provided from the table above (landmark name and location), we are then able to create a map using leaflet which will pinpoint the exact location of these places and label them on the resulting map.

```{r}
Landmarks_map <- leaflet(Landmarks_DC) %>% 
  addProviderTiles(providers$Stamen.TonerLite) %>% 
  setView(-77.0346613, 38.8935128, zoom = 12.5) %>% 
  addCircles(lng = ~Longitude,
             lat = ~Latitude,
             weight = 12,
             fillOpacity = 1) %>% 
  addControl("Location of DC Landmarks", position = "topright")

Landmarks_map

#Code above shows the 4 points mapped out on the DC map using the latitude and longitude provided from the dataset
#the points are weighted at 10 in order to be seen clearly with an opacity of 1, and "Location of DC Landmarks was placed in the corner of the map in order to explain what was being shown with the points on the map
```
