---
title: "Company Complaints Analysis"
description: |
  These charts and data tables pull out and visualize key elements of a consumer complaints report from 2020. 
author:
  - name: Arielle Ostry
    url: https://arielleostry.netlify.app/about.html
date: 04-13-2021
output:
  distill::distill_article:
    self_contained: false
categories:
  - financial
  - data
  - charts
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(janitor)
library(glue)
library(plotly)
library(DT)
library(kableExtra)
library(htmlwidgets)
library(htmltools)
library(readxl)

complaints <- readRDS("complaints.rds")
```

Complaints for this analysis were sourced from The Consumer Financial Protection Bureau (CFPB).

This first chart shows which companies had the most complaints out of the data selected. In order to create this visual, I first grouped the data by company and then arranged the companies in descending order. 

After filtering for the top three companies in this dataset, I created a bar graph using plot_ly.

### Chart 1

```{r}
Companies_with_most_complaints <- complaints %>% select(company) %>% 
                                group_by(company) %>%                                                 summarise(amount_complaints = n()) %>%                                 arrange(desc(amount_complaints))

Top3_complaints <- Companies_with_most_complaints %>% filter(amount_complaints>10000)

#the code above is isolating the company variable in the complaints dataset, we will use this simplified dataset to create a chart in plot_ly to visually show the top companies responsible for the complaints

fig1 <- plot_ly(data = Top3_complaints, x = ~amount_complaints, y = ~company, type = 'bar', name = '2020 Companies with the Most Complaints')

fig1 <- fig1 %>% layout(
                title = "2020 Companies with the Most Complaints",
                xaxis = list(title = "Number of Complaints"),
                yaxis = list(title = "")
)

fig1

#code above makes a bar graph which shows the three companies with the most complaints; I had trouble with making the companies themselves readable, but if you hover over the bars they pop up... maybe we could discuss this in class?


```

This second chart shows how companies tend to respond to complaints using a donut graph to show percentages out of the whole. I grouped by company response to the consumer and cleaned up the data by filtering out blank observations. 

I then created the donut graph using plot_ly.

### Chart 2

```{r}
#data prep - borrowed from initial analysis markdown file

company_response <- complaints %>% 
  select(company_response_to_consumer) %>% 
  group_by(company_response_to_consumer) %>% 
  summarise(r = n()) 

company_response_clean <- filter(company_response, r > 1)

#data visualization - donut chart to show the percentage of company responses to complaints

fig2 <- company_response_clean %>% plot_ly(labels = 
                    ~company_response_to_consumer, values = ~r)

fig2 <- fig2 %>% add_pie(hole = 0.6)

fig2 <- fig2 %>% layout(
                  title = "How companies respond to complaints",  
                  showlegend = F,
                  xaxis = list(showgrid = FALSE, zeroline = FALSE, 
                               showticklabels = FALSE),
                  yaxis = list(showgrid = FALSE, zeroline = FALSE, 
                               showticklabels = FALSE))
fig2

#experiencing a similar issue to fig1 where it is difficult to read some of the numbers without hovering over... not sure how to fix the situation... perhaps a legend would make more sense?
```
    
This third chart looks at the number of complaints throughout the year, so you can see which months had more complaints and which had less. 

In order to develop this graph, I added a month column to the dataset and grouped by it. 

The line graph was also made through plot_ly.

### Chart 3

```{r}
complaints_with_month <- complaints %>% mutate(month = month(date_received))

complaints_over_year <- complaints_with_month %>% group_by(month) %>%
  summarise(count_by_month = n()) %>% 
  select(month, count_by_month)

#organizes data into month and number of observations

fig3 <- plot_ly(complaints_over_year, x = ~month, y = ~count_by_month, type = 'scatter', mode = 'lines')

fig3 <- fig3 %>%  
  layout(title = 'Number of Complaints per Month', 
           yaxis = list(title = 'Number of Complaints'), 
          xaxis = list(title = 'Month') )
                       
fig3

#line graph shows number of complaints received per month throughout the year
```

